Supplement to Faithful Variable Screening for High-Dimensional Convex Regression

### 2016-03-09 tex/scam/additive_faithful.tex
minor typo

\begin{remark}
In Theorem~\ref{thm:convex_faithful}, we do not assume a parametric
form for the additive components; the additive approximations may not
be faithful if we take a parametric form. For example, suppose we
approximate a mean-zero convex function $f(X)$ by a linear form $X
\beta$. The optimal linear function in the population setting is
$\beta^* = \Sigma^{-1} \trm{Cov}(X, f(X))$ where $\Sigma = X^\tran X$ is the
covariance matrix. Suppose the $X$'s are independent, centered, and have a
symmetric distribution with unit variance, and suppose $f(\mathbf{x})
= x_1^2 - \E[X_1^2]$. Then $\beta^*_1 = \E[ X_1 f(X)] = \E[ X_1^3 -
  X_1 \E[X_1^2]] = 0$.
\end{remark}

>>>>

\begin{remark}
In Theorem~\ref{thm:convex_faithful}, we do not assume a parametric
form for the additive components; the additive approximations may not
be faithful if we take a parametric form. For example, suppose we
approximate a mean-zero convex function $f(X)$ by a linear form $X
\beta$. The optimal linear function in the population setting is
$\beta^* = \Sigma^{-1} \trm{Cov}(X, f(X))$ where $\Sigma = \E X^\tran X$ is the
covariance matrix. Suppose the $X$'s are independent, centered, and have a
symmetric distribution with unit variance, and suppose $f(\mathbf{x})
= x_1^2 - \E[X_1^2]$. Then $\beta^*_1 = \E[ X_1 f(X)] = \E[ X_1^3 -
  X_1 \E[X_1^2]] = 0$.
\end{remark}
